hbm_paper_results

### 2024-05-23 paper_main_results.Rmd
cleaning and updating

ven_plot <- ggplot(ven.df) +
  geom_jitter(data = raw_df, aes(x=raw_df$age_years, y=raw_df$Ventricles),  alpha=0.4, width=.2, color="lightgray") +
  #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
  geom_line(aes(x=age_years, y=centile_1, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_2, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_3, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_4, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_5, color=dataset, linetype=dataset), linewidth=1.5) +
  # geom_line(aes(x=age_years, y=centile_6, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_7, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_8, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_9, color=dataset, linetype=dataset)) +
  facet_wrap(~sex) + 
  scale_linetype_manual(values = c('raw'= "dotted", cf.gam = "solid", cf.gamlss = "solid", cf.lm = "longdash"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #scale_color_manual(values = c('raw'= "black", cf.gam = "#E84617", cf.gamlss = "#17E846", cf.lm = "purple")) +
  scale_color_manual(values = c('raw'= "black", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) + 
  theme_linedraw(base_size = 11) +
  geom_label(data=tmp_labels, aes(x=age_years, y=value, label=as.character(centile)), nudge_x = -0.75, size=3) +
  xlab("Age (days)") + ylab("Volume (mm3)") +
  labs(title="Ventricular volume brain charts")
```

@@

```{r}
fig_2 <- ggarrange(
  ven_plot,
  ggarrange(global_cent_errs_plot, p_diff, ncol=1, nrow=2, heights = c(1.2, 2), common.legend = FALSE, labels=c(NA, "C"), vjust = c(-0.25)),
  ncol=2, nrow=1, 
  labels=c("A", "B"),
  widths=c(1.1, 1)
  #hjust=0.01,
  # align = "hv"
  )

>>>>

ven_plot <- ggplot(ven.df) +
  geom_jitter(data = raw_df, aes(x=raw_df$age_years, y=raw_df$Ventricles),  alpha=0.4, width=.2, color="lightgray") +
  #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
  geom_line(aes(x=age_years, y=centile_1, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_2, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_3, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_4, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_5, color=dataset, linetype=dataset), linewidth=1.5) +
  # geom_line(aes(x=age_years, y=centile_6, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_7, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_8, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_9, color=dataset, linetype=dataset)) +
  facet_wrap(~sex) + 
  scale_linetype_manual(values = c('raw'= "dotted", cf.gam = "solid", cf.gamlss = "solid", cf.lm = "longdash"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #scale_color_manual(values = c('raw'= "black", cf.gam = "#E84617", cf.gamlss = "#17E846", cf.lm = "purple")) +
  scale_color_manual(values = c('raw'= "black", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) + 
  theme_linedraw(base_size = 11) +
  theme(plot.title = element_text(size=12), legend.position="bottom") +
  geom_label(data=tmp_labels, aes(x=age_years, y=value, label=as.character(centile)), nudge_x = -0.75, size=3) +
  xlab("Age (days)") + ylab("Volume (mm3)") +
  labs(title="Ventricular volume brain charts")
```

@@

```{r}
fig_2 <- ggarrange(
  ven_plot,
  ggarrange(global_cent_errs_plot, p_diff, ncol=1, nrow=2, heights = c(1.2, 2), common.legend = FALSE, labels=c(NA, "C"), vjust = c(-0.25)),
  ncol=2, nrow=1, 
  labels=c("A", "B"),
  widths=c(1.2, 1)
  #hjust=0.01,
  # align = "hv"
  )
